Executive Constraints and Civil Conflict

### 2019-08-04 paper.Rmd
WIP: add some initial plots

---
title: Executive Constraints and Civil Conflict
author: J.L.A. Krusell
output: pdf_document
---

\[ x_{j}^{obs} \sim \mathsf{Normal}(x_{j}^\ast, \sigma_{j}^{obs}) \]
\[ x_{ji}^\ast \sim \mathsf{Normal}(\gamma_j + \lambda_j \theta_i, \psi_j) \]
\[ \theta \sim \mathsf{Normal}(0, 1) \]

>>>>

---
title: Executive Constraints and Civil Conflict
author: J.L.A. Krusell
output:
    pdf_document:
        pandoc_args: ["--syntax-definition", "stan.xml",
                      "--highlight-style", "kate"]
---

```{r, echo = F}
```

\[ y_t \sim \mathsf{Bernoulli}(\pi_t) \]
\[ \pi_t = F(\alpha + \beta \theta_{t-1} + \delta_k + GP(t)) \]
\[ \delta_k \sim \mathsf{Normal}(0, \sigma) \]
\[ \sigma \sim \mathsf{HalfCauchy}(0, 1) \]
\[ x_{jt}^\ast \sim \mathsf{Normal}(\gamma_j + \lambda_j \theta_t, \psi_j) \]
\[ x_{j}^{obs} \sim \mathsf{Normal}(x_{j}^\ast, \tau_{j}^{obs}) \]
\[ \theta \sim \mathsf{Normal}(0, 1) \]
\[ \lambda \sim \mathsf{Lognormal}(0, 1) \]
\[ \gamma \sim \mathsf{Normal}(0, 5) \]
\[ \psi \sim \mathsf{HalfCauchy}(0, 1) \]

We assume local item independence such that the residual variances, $\psi$, are uncorrelated.

- v2lginvstp - Legislature investigates in practice
- v2lgfunds - Legislature controls own resources
- v2lgqstexp - Legislature questions officials in practice
- v2lgoppart - Legislature opposition parties able to exercise oversight

- v2juhcind - High court independence
- v2juncind - Lower court independence
- v2juhccomp - Compliance with higher court
- v2jucomp - Compliance with judiciary

- v2exrescon - Executive respects constitution
- v2lgotovst - Executive oversight

## Analysis

```{r, echo = F}
suppressMessages(library(bayesplot))
suppressMessages(library(rstan))

fit <- readRDS("posteriors/fit.rds")
beta <- as.matrix(fit, pars = "beta")
```

```{r, echo = F}
color_scheme_set("green")
mcmc_intervals(beta, point_est = "median") +
    vline_0(size = 0.25, linetype = 2, color = "violet") +
    ggplot2::scale_y_discrete(labels = c("Executive Constraints",
                                "State Capacity",
                                "Executive Constraints:State Capacity",
                                "GDP per Capita Growth",
                                "Population Density",
                                "Mean Elevation",
                                "Relevant Ethnic Groups",
                                "Neighbouring Conflict",
                                "Peace Years Logged"))

```

\newpage

# Appendix

## Stan Code

```{stan, code=readLines("stan/model.stan"), eval=FALSE, output.var="x"}
```
\newpage

## GAM Model

```{R, echo = F, results = "asis"}
ml <- readRDS("data/gam_model.rds")
itsadug::gamtabs(ml, caption = "GAM Model")
```

```{R, echo = F}
p <- predict(ml, type = "response")

plot(density(p[ml$model$lepisode_onset == 0]), col = "lightblue",
     main = "Predicted Probability Densities")
lines(density(p[ml$model$lepisode_onset == 1]), col = "indianred")
```

```{R, echo = F}
caTools::colAUC(p, ml$model$lepisode_onset, plotROC = T)
```
